%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Short Sectioned Assignment
% LaTeX Template
% Version 1.0 (5/5/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Frits Wenneker (http://www.howtotex.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[paper=a4, fontsize=11pt]{scrartcl} % A4 paper and 11pt font size

\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\usepackage{fourier} % Use the Adobe Utopia font for the document - comment this line to return to the LaTeX default
\usepackage[english]{babel} % English language/hyphenation
\usepackage{amsmath,amsfonts,amsthm} % Math packages

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage{graphicx} % Required for including pictures
\usepackage{wrapfig}
\usepackage{float}

\usepackage[top=.9in, bottom=.9in, left=1in, right=1in]{geometry}

\usepackage{sectsty} % Allows customizing section commands
\allsectionsfont{\normalfont\scshape} % Make all sections centered, the default font and small caps

\usepackage{fancyhdr} % Custom headers and footers
\pagestyle{fancyplain} % Makes all pages in the document conform to the custom headers and footers
\fancyhead{} % No page header - if you want one, create it in the same way as the footers below
\fancyfoot[L]{} % Empty left footer
\fancyfoot[C]{} % Empty center footer
\fancyfoot[R]{\thepage} % Page numbering for right footer
\renewcommand{\headrulewidth}{0pt} % Remove header underlines
\renewcommand{\footrulewidth}{0pt} % Remove footer underlines
\setlength{\headheight}{0pt} % Customize the height of the header

\numberwithin{equation}{section} % Number equations within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{figure}{section} % Number figures within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{table}{section} % Number tables within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)

\setlength\parindent{0pt} % Removes all indentation from paragraphs - comment this line for an assignment with lots of text

\graphicspath{{./graphics/}} % Specifies the directory where pictures are stored

%----------------------------------------------------------------------------------------
%   TITLE SECTION
%----------------------------------------------------------------------------------------

\newcommand{\horrule}[1]{\rule{\linewidth}{#1}} % Create horizontal rule command with 1 argument of height

\title{ 
\normalfont \normalsize 
\textsc{6.885 From ASCII to Answers} % Your university, school and/or department name(s)
\horrule{0.5pt} % Thin top horizontal rule
\large The Librarian: Entity Matching Across Media Types % The assignment title
\horrule{1pt} % Thick bottom horizontal rule
}

\author{Joshua Blum, Nolan Eastin \\ \{joshblum, neastin\}@mit.edu}

\date{\normalsize\today} % Today's date or a custom date
\begin{document}

\maketitle % Print the title

\section{Introduction and Motivation}
%TODO
%------------------------------------------------
Entity matching is nontrivial and especially difficult when each entity is large. The Librarian aims to perform automatic entity resolution across various media types. Given sets of text, audio, image, and video files, The Librarian can merge the sets of entities by deduplicating the files, gathering metadata from trusted sources, (i.e. IMDB, Rotten Tomato, and Spotify APIs), and categorizing the media based on the metadata that is found. \\

The motivation behind the system is to be able to handle large dumps of data as well as incremental updates over a large corpus of files with many contributers. The Librarian serves as a background system upon which clients can be built which handler user interaction to add and modify data within the system.\\

The initial system has been tested with approximately 6 TB of seed data that has been collected from several sources. This data was used as training data for testing and developing our matching algorithms. Only movie entities were categorized from this corpus, although the matching algorithms can be extended to work with other media types such as audio, image, or text files.

In addition to trying to algorithmically resolve two entities, crowd sourcing is used to establish ground truth where necessary. If there are multiple matches for a single entity a user can select the correct metadata for the entity or input their own.\\

We begin by discussing related work (\ref{sec:related-work}), providing a system design overview (\ref{sec:system-overview}), showing an analysis of the system's performance (\ref{sec:performance}), list goals for future work (\ref{sec:future-work}), and conclusions of the project (\ref{sec:conclusions}).

\section{Related Work}
\label{sec:related-work}
%------------------------------------------------
Shazam

Shazam is a widely known service that specializes in identifying songs. Shazam has the ability to create audio fingerprints from given audio files or samples. They initially built a large database of audio fingerprints from thousands of sounds to use as ground truth. 

They then query users for a 10 second audio sample, and they are able to generate an audio fingerprint from these and cross-match with their large data sample. An important part of their service is that they have the ability to use the service even with background noise. Shazam uses different filtering algorithms to reduce background noise and get better samples. 

Additionally, in order to prevent enormous data storage - (think every song times large amount of time sliding windows) they developed a method of fingerprinting audio samples based on tone intensity, which allowed them to get more representative 

Audible Magic [ music/tv audio fingerprinting ]




\section{System Overview}
\label{sec:system-overview}
The Librarian is architected to accept jobs over a local HTTP server and ingest them into the system. A job consists of a single entity to be identified. Following the flow of Figure \ref{fig:system-overview} a job is first queued and then consumed by a worker process. Worker processes then identify the entity type and apply the handler for this type. The system currently only accepts movie entities, however this can extended to allow multiple handlers by using file extensions to differentiate entity types. A handler type then performs two steps to ingest the entity, first a deduplication step, and if the entity is not a duplicate, an identification step. Deduplication looks at the internal metadata store of The Librarian whereas identification looks at outside sources to establish ground truth. The details of these algorithms are discussed further for the movie entity type.

data added to metastore, job_id maps to metadata_id

%------------------------------------------------

\subsection{Deduplication}
\label{sec:deduplication}

\subsubsection{Movie Entities}
\label{sec:dedup-movie-entities}
The deduplication process for movie entities consists of two steps. First a md5 hash is computed across the contents of the file and the metadata store is checked for any matches. This approach is brittle since the duplicate entities can still appear if two instances of the same film are added with different resolutions. A more flexible approach is to compute an audio fingerprint. We compute a fingerprint across a subsection of the file (first 10 minutes) since only a short duration is needed and the running time for computing a fingerprint across the entire file increases exponentially with file size. 

%%nolan add paragraph about audio fingerprinting


%------------------------------------------------

\subsection{Implementation}
\label{sec:implementation}
%TODO

%------------------------------------------------
\subsubsection{Handlers}
\label{sec:handlers}
%TODO

%------------------------------------------------
\subsubsection{Identifiers}
\label{sec:identifiers}
%TODO

%------------------------------------------------

\section{Performance}
\label{sec:performance}
%TODO

%------------------------------------------------

\section{Future Work}
\label{sec:future-work}
%TODO

%------------------------------------------------
\section{Conclusions}
\label{sec:conclusions}
%TODO

%------------------------------------------------


\end{document}`'